Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
zip

These two questions have been challening to address because for a long
time it was difficult to produce realistic galactic discs within the
CDM context \citep{1997ApJ...478...13N}.
The success of such enterprise has been the result of high numerical
resolution and the understanding that baryonic effects such as stellar
feedback and black hole feedback play an important role in forming a
galactic disc resembling the Milky Way.
Along the way, many numerical experiments have also show that the baryonic
effects also impact the dark matter halo shape making the halo rounder
than it otherwise be in a dark matter only simulation
\citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
But only few simulations have presented detailed results on the
radial evolution of the alignment between the stellar disc and the
dark matter halo \citep{Bailin05,Debattista13}.

Observational constraints of the dark matter halo have been in
tension and rapidly evolving during the last decade. 
One can find studies favoring prolate
\citep{Banerjee_and_Chanda_2011,Bowden_et_al._2016},  oblate
\citep{LM10,Deg_and_Widrow_2013,Vera-Ciro_and_Helmi_2013} and
spherical configurations \citep{Bovy16}.  
Constraints from modeling of stellar streams discard the prolate
configuration \citep{LM10,Pearson_et_al._2015,Bovy16} although some other studies
still doubt that stellar streams can be used to constrain the halo
shape once other assumptions, such as the density profile, are relaxed
\citep{Ibata_et_al._2013}.

>>>>

These two questions have been challening to address because for a long
time it was difficult to produce realistic galactic discs within the
CDM context \citep{1997ApJ...478...13N}.
The success of such enterprise has been the result of high numerical
resolution and the understanding that baryonic effects such as stellar
feedback and black hole feedback play an important role in forming a
galactic disc resembling the Milky Way.
Along the way, many numerical experiments have also show that the baryonic
effects also impact the dark matter halo shape making the halo rounder
than it otherwise be in a dark matter only simulation
\citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
But only few simulations have presented detailed results on another
important aspect of the disc-halo relationship, namely, the radial
evolution of the alignment between the stellar disc and the dark
matter halo \citep{Bailin05,Debattista13}.

Observational constraints of the dark matter halo
have also been in tension and rapidly evolving during the last decade.  
One can find studies favoring prolate
\citep{Banerjee_and_Chanda_2011,Bowden_et_al._2016},  oblate
\citep{LM10,Deg_and_Widrow_2013,Vera-Ciro_and_Helmi_2013} and
spherical configurations \citep{Bovy16}.  
Constraints from modeling of stellar streams discard the prolate
configuration \citep{LM10,Pearson_et_al._2015,Bovy16} although some other studies
still doubt that stellar streams can be used to constrain the halo
shape once other assumptions, such as the density profile, are relaxed
\citep{Ibata_et_al._2013}.
